Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-12 popl24/automation.tex
checkpoint

Any marginalization or conditioning of $\progtt(\prog)$ can be easily
obtained algorithmically, in particular $\progd(\prog) =
\margd{\progtt(\prog)}{\iov(\prog)}$.  As already discussed in Section
\ref{section-hyperprop} and as we will discuss more below, extensional
and intensional security properties are predicated on marginalizations
and conditionings of basic distributions. So calculating
$\runs(\prog)$ establishes the foundation for our analysis.

@@

Given computation of $\prog(\prog)$ for programs $\prog$, we can
immediately observe that the extensional hyperproperties discussed in
Section \ref{section-hyperprop} are certifiable.
\begin{lemma}
  Both $\pni$ (Definition \ref{definition-PNI}) and $\NIMO$ (Definition \ref{definition-NIMO}) are certifiable. 
\end{lemma}

@@

\subsection{Certification of Composable Intensional Properties}
\label{section-automation-intensional}

@@

Our solution is to design gate certifications that demonstrably
guarantee security for circuits built from them. Intuitively, we can
consider any gate as a mini-program and certify intensional properties
of its isolated program distribution. These intensional properties are
guaranteed secure in circuit compositions, as we demonstrate using
methods based on probabilistic separation logic
\ref{barthe2019probabilistic}. While this last step is manual, our
gate certifications are defined generally and can be used to certify
new gate implementations, and verification applies to a circuit of any
size. In Section \ref{section-composition} we will demonstrate our
approach using YGC and GMW as examples.

When we consider intensional properties
of gates in isolation, we will explicitly consider flip conditions in
distributions. Thus we will be directly concerned with basic distributions,
which we denote $\progtt(\prog)$, and we will often focus on views
defined in subprotocols. 
Notions of probabilistic independence, aka \emph{separation}, as well
as correlation, are important to certify. We borrow the symbols $*$
and $\sim$ from \cite{barthe2019probabilistic} with the same
denotations.
\begin{definition}
  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pmf}{X}{Y}$ iff for all
    $\store \in \mems(X \cup Y)$ we have
  $\margd{\pmf}{X \cup Y}(\store) =
  \pmf(\store_X) * \pmf(\store_Y)$
\end{definition}
We immediately observe that separation and correlation are certifiable,
since they are based on marginalization and conditioning of program
distributions. 
\begin{lemma}
  \label{lemma-autosep}
  Both of the following are true:
  \begin{enumerate}
  \item $\sep{\progtt(\prog)}{X}{Y}$ is certifiable for any $X$ and $Y$.
  \item $\vc{\progtt(\prog)}{x}{y}$ is certifiable for any $x$ and $y$.
  \end{enumerate}
\end{lemma}

>>>>

Any marginalization or conditioning of $\progtt(\prog)$ can be easily
obtained algorithmically, in particular $\progd(\prog) =
\margd{\progtt(\prog)}{\iov(\prog)}$.  As already discussed in Section
\ref{section-hyperprop} and as we will discuss more below,
crucial properties are predicated on marginalizations
and conditionings of basic distributions. So calculating
$\runs(\prog)$ establishes the foundation for our analysis.

@@

Given computation of $\prog(\prog)$ for programs $\prog$, we can
immediately observe that the security hyperproperties discussed in
Section \ref{section-hyperprop} are certifiable.
\begin{lemma}
  Both $\pni$ (Definition \ref{definition-PNI}) and $\NIMO$ (Definition \ref{definition-NIMO}) are certifiable. 
\end{lemma}

@@

\subsection{Certification of Composable Properties}
\label{section-automation-intensional}

@@

Our solution is to design gate certifications that demonstrably
guarantee security for circuits built from them. Intuitively, we can
consider any gate as a mini-program and certify properties
of its isolated program distribution. These component properties are
guaranteed secure in circuit compositions, as we demonstrate using
methods based on probabilistic separation logic
\ref{barthe2019probabilistic}. While this last step is manual, our
gate certifications are defined generally and can be used to certify
new gate implementations, and verification applies to a circuit of any
size. In Section \ref{section-composition} we will demonstrate our
approach using YGC and GMW as examples.

When we consider properties
of gates in isolation, we will explicitly consider flip conditions in
distributions. Thus we will be directly concerned with basic distributions,
which we denote $\progtt(\prog)$, and we will often focus on views
defined in subprotocols. 
Notions of probabilistic independence, aka \emph{separation}, as well
as correlation, are important to certify. We borrow the symbols $*$
and $\sim$ from \cite{barthe2019probabilistic} with the same
denotations.
\begin{definition}
  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pmf}{X}{Y}$ iff for all
    $\store \in \mems(X \cup Y)$ we have
  $\margd{\pmf}{X \cup Y}(\store) =
  \pmf(\store_X) * \pmf(\store_Y)$
\end{definition}
We immediately observe that separation and correlation are certifiable,
since they are based on marginalization and conditioning of program
distributions. 
\begin{lemma}
  \label{lemma-autosep}
  Both of the following are true:
  \begin{enumerate}
  \item $\sep{\progtt(\prog)}{X}{Y}$ is certifiable for any $X$ and $Y$.
  \item $\vc{\progtt(\prog)}{x}{y}$ is certifiable for any $x$ and $y$.
  \end{enumerate}
\end{lemma}
